---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2023

<!-- badges: start -->
[![R-CMD-check](https://github.com/yywwwyy/bis620.2023/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/yywwwyy/bis620.2023/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/yywwwyy/bis620.2023/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/yywwwyy/bis620.2023/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/yywwwyy/bis620.2023/actions/workflows/lint.yaml/badge.svg)](https://github.com/yywwwyy/bis620.2023/actions/workflows/lint.yaml)
<!-- badges: end -->

This bis620.2023 package is designed to facilitate the analysis and visualization of clinical trial data from ctgov. It includes a Shiny application (app.R) and a suite of functions that streamline the process of querying, processing, and presenting clinical trials research data.

## Installation(takes nearly 30 mins, please be patient)
###

You can install the development version of bis620.2023 from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
#devtools::install_github("yywwwyy/bis620.2023")
```
## Features
calculate_duration.R: Calculate the duration between clinical trial start and end dates.
data.R: Data preparation and transformation utilities.
exclude_query.R: Functionality to exclude certain queries from the data set.
get_concurrent_trials.R: Identify concurrent clinical trials.
globals.R: Define global variables for use within the Shiny app.
hello.R: A simple function demonstrating package use.
intervention_and_outcome_data_pro.R: Process data related to interventions and outcomes.
plot_condition_histogram.R: Plot histograms of conditions from clinical trial data.
plot_phase_histogram.R: Visualize the different phases of clinical trials.
plot.R: General plotting functions.
query_kwds.R: Functions to query the data set with specific keywords.
show_info.R: Display information about specific clinical trials.
spectral.R: Perform spectral analysis on data.

## How to run shinyapp
library(bis620.2023)

runshinyapp()


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bis620.2023)
## basic example code
accel |> 
  head(100) |> 
  plot_accel()

studies |> head(1000)|>
   exclude_query("Rates, Pembrolizumab","brief_title")
calculate_duration("2020-01-01", "2020-01-31", "days")
calculate_duration("2020-01-01", "2020-02-01", "months")
calculate_duration("2020-01-01", "2021-01-01", "years")
plot_map(studies)
plot_country_histogram(studies)
```

### link to the coverage page and lint results
# [R-CMD-check]https://github.com/yywwwyy/bis620.2023/actions/workflows/R-CMD-check.yaml
# [test-coverage]https://github.com/yywwwyy/bis620.2023/actions/workflows/test-coverage.yaml
# [lint]https://github.com/yywwwyy/bis620.2023/actions/workflows/lint.yaml
